Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-02-05 msc-publication.tex
tweak intro to identify TF and cut cells earlier on

There are two main approaches to represent orography on a grid.  With terrain following (TF) layers the terrain's influence decays with height: the bottommost layers follow the underlying surface closely while the uppermost layers are flat.  TF layers are usually implemented on a rectangular computational grid using transformed coordinates.

>>>>

There are two main approaches to represent orography on a grid: terrain following layers, and cut cells.  With terrain following (TF) layers the terrain's influence decays with height so that the bottommost layers follow the underlying surface closely while the uppermost layers are flat.  TF layers are usually implemented on a rectangular computational grid using transformed coordinates.
